\documentclass[11pt,a4paper]{article}
  \usepackage[utf8]{inputenc}
  \usepackage[left=1.5cm,right=1.5cm,top=1.5cm,bottom=1.5cm]{geometry}
  \usepackage{enumitem}
  \usepackage{hyperref}
  \usepackage{titlesec}
  \usepackage{xcolor}

  % Formatting
  \pagestyle{empty}
  \setlist{nolistsep}
  \titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
  \titleformat{\subsection}{\bfseries}{}{0em}{}

  % Custom colors
  \definecolor{linkcolor}{RGB}{0,0,139}
  \hypersetup{
      colorlinks=true,
      linkcolor=linkcolor,
      urlcolor=linkcolor,
  }

  \begin{document}

  % Header
  \begin{center}
      {\LARGE \textbf{Nikhil Singh}} \\[0.3em]
      {\large Principal AI Architect} \\[0.5em]
      Stockholm, Sweden \\[0.3em]
      \href{mailto:nikhilsingh2009@gmail.com}{nikhilsingh2009@gmail.com} $|$
      \href{https://linkedin.com/in/singh-nikhil}{singh-nikhil} $|$
      \href{https://nikhilsingh.io/}{https://nikhilsingh.io/}
  \end{center}

\section*{Professional Summary}
\small
Principal AI Architect \& Product Leader with 12+ years of experience scaling AI products for global FinTech and Retail leaders. Specialises in translating technical capabilities (from LLMs to Knowledge Graphs) into actionable product roadmaps that drive measurable business value. A pragmatic leader who unites engineering and product teams, navigating technical trade-offs to ship AI solutions that are as commercially viable as they are technically robust. A technical authority combining architectural depth with commercial acumen to ensure AI investments are scalable, profitable, and aligned with core business goals.

% --- Experience ---
\section*{Professional Experience}

\noindent \textbf{Klarna Bank AB} \hfill Stockholm, Sweden \\
\textit{Principal Data Scientist} \hfill Apr 2025 -- Present
\begin{itemize}[leftmargin=*, label=\textbullet]
    \item \textbf{Enterprise Intelligence \& Search:} Leading the development of an AI-native workflow engine to quantify company-wide task impact. Personally architected a zero-downtime migration of \textbf{1M+ workflows} (moving from unstructured JSONB to normalised Postgres schemas) to ensure 24/7 reliability as the organisation's single source of truth.
    \begin{itemize}[label=$\circ$]
    \item \textit{Impact:} Central workflow engine for \textbf{$\sim$4,000 employees}, delivering \textbf{\$18M USD in annualized productivity gains} via automated dependency mapping and ticket resolution.
\end{itemize}
    \smallskip
    \item \textbf{GenAI Infrastructure \& Strategy:} Architected a proprietary LLM fine-tuning platform (integrating LangSmith/NVIDIA Triton) to benchmark B2B/B2C models. Transitioned the organisation from proprietary models to an open-source strategy (Llama Instruct/GPT-OSS120b) using LoRA adapters.
    \begin{itemize}[label=$\circ$]
        \item \textit{Impact:} Accelerated the Shopping Assistant launch by \textbf{4 months} and reduced inference costs by \textbf{$>$ \$7M USD}. Optimised system latency to \textbf{sub-second} performance (industry-leading for agentic workflows) while maintaining data sovereignty through in-house GPU deployment.
    \end{itemize}
\end{itemize}

\vspace{0.5em}

\noindent \textbf{Klarna Bank AB} \hfill Stockholm, Sweden \\
\textit{Lead Data Scientist} \hfill Apr 2023 -- Apr 2025
\begin{itemize}[leftmargin=*, label=\textbullet]
    \item \textbf{Product Strategy \& Revenue Growth:} Orchestrated the product roadmap for the ``Buy Again'' recommendation engine, translating lifecycle behaviour analysis into a high-impact feature that drove a \textbf{27\% increase in purchase rates} and \textbf{5\% overall volume growth}.
    \item \textbf{Technical Architecture \& Innovation:} Architected Klarna's foundational Customer Intelligence Graph, integrating NER and Large Language Models (T5) to unify transactional and behavioural data into a 360-degree customer view, enabling cross-functional personalisation use cases.
    \item \textbf{Operational Efficiency:} Defined the automation strategy for Legal-Regulatory compliance, leading the deployment of NLP-based document extraction tools that significantly reduced manual review time and streamlined compliance workflows.
    \item \textbf{Scale \& Performance:} Directed the optimisation of the core personalisation engine (500M+ SKUs) using Deep Learning (DSSM), achieving \textbf{260--450\% improvement in CTR} and \textbf{18\% DAU growth} by aligning technical segmentation with user engagement metrics.
    \item \textbf{Commercial Impact:} Spearheaded the integration of affiliate merchant data into the business index via Neural Collaborative Filtering, directly generating \textbf{36M SEK in affiliate revenue} (Dec 2023) through improved inventory visibility.
\end{itemize}

\newpage

\noindent \textbf{Klarna Bank AB} \hfill Stockholm, Sweden \\
\textit{Senior Data Scientist} \hfill Aug 2020 -- Mar 2023
\begin{itemize}[leftmargin=*, label=\textbullet]
    \item \textbf{System Design:} Conceptualised and delivered Klarna’s first Product Group Recommendation System, establishing the technical standard for user-similarity engines across 98 diverse merchant ecosystems.
    \item \textbf{Advanced R\&D:} Pioneered the application of multimodal learning (OpenAI CLIP) for catalog normalisation, solving critical data sparsity issues and enabling high-fidelity customer preference categorisation.
    \item \textbf{Mentorship:} Established a structured mentorship program for junior data scientists and led internal hackathons, fostering a culture of technical excellence and rapid prototyping.
\end{itemize}

\vspace{0.5em}

\noindent \textbf{o9 Solutions, Inc.} \hfill Bangalore, India \\
\textit{Senior Data Scientist} \hfill Apr 2020 -- July 2020
\begin{itemize}[leftmargin=*, label=\textbullet]
    \item \textbf{Presales \& Solutioning:} Led the technical solutioning for a major supply chain prospect, designing an AI-driven forecasting architecture that successfully converted the pilot into a confirmed partnership.
\end{itemize}

\vspace{0.5em}

\noindent \textbf{Ascena Retail Group (GIC)} \hfill Bangalore, India \\
\textit{Data Scientist} \hfill Jan 2018 -- Mar 2020
\begin{itemize}[leftmargin=*, label=\textbullet]
    \item \textbf{Forecasting at Scale:} Engineered a TensorFlow-based store traffic forecasting model deployed via Apache Beam/GCP, achieving \textbf{$<$8\% MAPE} and directly informing labour allocation for physical stores.
    \item \textbf{Pricing Strategy:} Developed Price Elasticity and Customer Lifetime Value (CLV) models using Random Survival Trees, improving marketing campaign uplift by \textbf{70\%+} through targeted intervention strategies.
\end{itemize}

\vspace{0.5em}

\noindent \textbf{Diet Code} \hfill Bangalore, India \\
\textit{Data Scientist} \hfill Dec 2016 -- Dec 2017
\begin{itemize}[leftmargin=*, label=\textbullet]
    \item \textbf{Recommendation Systems:} Engineered the core recommendation algorithms for the NewsCase app, utilising matrix factorisation to drive a \textbf{15\% increase in user engagement}.
\end{itemize}

\vspace{0.5em}

\noindent \textbf{Cognizant Technology Solutions} \hfill India \\
\textit{Senior Consultant - Analytics} \hfill May 2016 -- Dec 2016
\begin{itemize}[leftmargin=*, label=\textbullet]
    \item \textbf{Search Optimisation:} Revamped the internal talent search engine using NLP (POS tagging), improving candidate matching accuracy from \textbf{32\% to 47\%}.
\end{itemize}

\vspace{0.5em}

\noindent \textbf{Nucleus Software Exports Ltd.} \hfill Noida, India \\
\textit{Software Engineer} \hfill July 2012 -- June 2014
\begin{itemize}[leftmargin=*, label=\textbullet]
    \item \textbf{Core Engineering:} Developed modules for the flagship lending product, managing change requests and high-volume data processing for banking clients.
\end{itemize}

% --- Education ---
\section*{Education}
\noindent \textbf{Indian Institute of Management Tiruchirappalli (IIM-T)} \hfill 2014 -- 2016 \\
MBA (PGPM)

\vspace{0.5em}

\noindent \textbf{UP Technical University} \hfill 2008 -- 2012 \\
B.Tech (Computer Science and Engineering)

% --- Technical Skills ---
\section*{Technical \& Strategic Toolkit}
\begin{itemize}[leftmargin=*, label=\textbullet]
    \item \textbf{Strategic Leadership:} AI Product Strategy, Road-mapping, Stakeholder Management, Tech Hiring, Translating Tech to Business Value.
    \item \textbf{Generative \& Agentic AI:} Agentic Workflows (ReAct, Planning, Tool Use), LLMs (GPT, Llama), RAG, Fine-tuning (LoRA, Adapters), LangSmith.
    \item \textbf{Core AI \& Algorithms:} Recommender Systems (Two-Tower, Neural CF), Reinforcement Learning (MDP, Q-learning), Graph NNs, Causal Inference (SHAP).
    \item \textbf{Customer Intelligence:} Customer Lifetime Value (CLV), Churn Prediction, RFM Segmentation, Price Elasticity, Behavioral Cohort Analysis.
    \item \textbf{Engineering Stack:} Python (PyTorch, TensorFlow, Scikit-learn), Spark, AWS/GCP (SageMaker Pipelines, Athena), Docker, MLOps.
    \item \textbf{Data Stores:} Vector (Pinecone), Graph (Neo4j), Relational/OLAP (Postgres, DuckDB, BigQuery).
\end{itemize}

\end{document}